\mytitile\\~

### 2019-10-04 document.tex
Small fix for scheme and introduction continued

A quantum system exposed to external driving can experience a number of quantum phenomena due to the resonant transitions between energy levels. The most known examples are coherent population trapping, electromagnetically induced transparency (EIT)\cite{boller1991observation}, stimulated Raman adiabatic passage\cite{bergmann1998coherent} and Autler-Townes (AT) splitting\cite{autler1955stark} which can happen in systems with just three energy levels. 
The main attention in our work is paid to the last effect, which related to the dressed states.
The AT effect has been studied in atomic\cite{picque1976direct} and molecular systems\cite{tamarat1995pump}, quantum dots\cite{xu2007coherent}, and superconducting qubits\cite{li2011decoherence, novikov2013autler}.

If the driving field is strong the interaction between the system and the field become significant and leads to oscillates with Rabi frequency. The new energy state called dressed states. If an additional weak probing field is applied, the spectra of the strongly driven system can be probed. In particular the dressed state model nicely explains the emergence of the Mollow triplet\cite{newstein1968spontaneous} spectrum, which consists of a central peak with two side bands separated by the Rabi frequency.

>>>>

In general, a quantum system exposed to strong external driving can experience various quantum phenomena explained by resonant single- and multi-photon transitions between energy levels. The most known examples are coherent population trapping, electromagnetically induced transparency (EIT)\cite{boller1991observation}, stimulated Raman adiabatic passage\cite{bergmann1998coherent} and Autler-Townes (AT) splitting\cite{autler1955stark} which can happen in systems with just three energy levels.

Our work is focused on the last effect, which has been studied in atomic\cite{picque1976direct}, molecular systems\cite{tamarat1995pump}, quantum dots\cite{xu2007coherent}, and also was observed for SAAs in several experiments\cite{baur2009measurement, sillanpaa2009autler, novikov2013autler, suri2013observation, peng2018vacuum}.

The main cause of the AT effect is the dressing of the atomic levels by strong EM radiation. This dressing The new energy state called dressed states. If an additional weak probing field is applied, the spectra of the strongly driven system can be probed. In particular the dressed state model nicely explains the emergence of the Mollow triplet\cite{newstein1968spontaneous} spectrum, which consists of a central peak with two side bands separated by the Rabi frequency.
